%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{fontawesome}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated  % Print the Last Updated text at the top right

\namesection{Varan}{Culanathan}{ % Your name
% \urlstyle{same}\url{http://linkedin.com/vculanathan} \\ % Your website, LinkedIn profile or other web address
\footnotesize  \faMobile \hspace{1mm} { (603)-257-5957 } \hspace{1mm}|\hspace{1mm} \faEnvelope \hspace{1mm} \href{mailto:vculanathan@umass.edu}{ vculanathan@umass.edu }\hspace{1mm}|\hspace{1mm} \faGithub \hspace{1mm} \href{https://github.com/vculanathan}{ github.com/vculanathan} \hspace{1mm}|\hspace{1mm}
\faLinkedinSquare \hspace{1mm} \href{https://www.linkedin.com/in/vculanathan}{linkedin.com/in/vculanathan} \\% Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{UMass Amherst}

\descript{B.S. in Computer Science}
\location{Expected May 2018 | Amherst, MA }
Dean's List (All Semesters) \\
\location{ Cum. GPA: 3.98 / 4.00 }
\sectionspace % Some whitespace after the section



%------------------------------------------------

%------------------------------------------------
% Links
%------------------------------------------------

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}
\textbullet{} Software Engineering \\
\textbullet{} Discrete Mathematics \\
\textbullet{} Introduction to Probability \\
\textbullet{} Functional Programming \\
\textbullet{} Data Structures \\


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Languages}


\location{\bf Proficient:}
Java | Shell | Python | SQL | \LaTeX\ \\ 
\vspace{2mm}
\location{\bf Familiar:}
C | Scala | HTML/CSS | Javascript \\


\sectionspace % Some whitespace after the section

\section{Engineering}


{\bf Infrastructure:}
AWS | Ansible | Docker | Jenkins | Terraform | Teleport \\  
{\bf Databases:}
MongoDB | SQL \\
{\bf Backend:} 
NodeJS \\
{\bf Native:}
Android

\sectionspace % Some whitespace after the section

\section{Awards}
{\bf Course Citation \hfill 2017} \\ 
\textit{Discrete Mathematics} \\ 
Ranked amongst the top 15 students in a class of over 200 students\\
\vspace{2mm}
{\bf Course Citation \hfill 2016} \\ 
\textit{Computer System Principles} \\ 
Ranked \#2 in a class of over 150 students\\
\vspace{2mm}
{\bf Course Citation \hfill 2015} \\ \textit{Data Structures} \\
 Ranked \#4 in a class of over 150 students\\
 \vspace{2mm}

\section{Projects} 
\textbullet{} {\bf Minesweeper \hfill June 2016} \\ A complete version of Minesweeper with fully functioning GUI and custom art. {\it Java} \\
\textbullet{} {\bf KeyFinder\hfill Jan 2015} \\ Control a person in a two-dimensional maze to find a hidden key. {\it Android Studio, Java} 
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.65\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Work Experience}

\sectionspace % Some whitespace after the section
\runsubsection{TriNetX}
\descript{| Software Engineering Intern}
\location{May 2016 – Sept 2016 | Cambridge, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Improved and increased automation of appliance provisioning process.
\item Created a set of utility scripts to obtain the health status of appliances based on network connectivity, port connectivity, and NIC bond configuration.
\item Performed ad-hoc tasks to improve monitoring and maintenance of AWS. 
\item Refactored codebase and helped create a custom Sonarqube profile to maintain cleanliness of future code.
\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{UMass Amherst}
\descript{| Teaching Assistant / Grader}
\location{Sept 2016 – Jan 2017 | Amherst, MA} 
\begin{tightitemize}
\item Help lead discussion sections with other TAs and meet weekly with Professor to modify and improve discussion sections to suit students’ needs
\item Grade homework and project submissions by students
\end{tightitemize}

\sectionspace % Some whitespace after the section
\runsubsection{TriNetX}
\descript{| Implementation Analyst Intern}
\location{May 2016 – Sept 2016 | Cambridge, MA}
\begin{tightitemize}
\item Designed and implemented feature to export audit and query history pages to CSVs. 
\item Wrote and Tested SQL Scripts to assess the cleanliness of healthcare organizations’ databases.
\item Completed data refreshes, data ingestion, and data mapping of healthcare organizations' data.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

%------------------------------------------------

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{RBR Labratory}
\descript{| Research Assistant}

\location{Oct 2015 – May 2016 | Ithaca, NY}
\begin{tightitemize}
\item Worked under Professor \textbf{\href{http://rbr.cs.umass.edu/shlomo/}{Shlomo Zilberstein}} to investigate the methodology used to calculate the impact factor of a journal.
\item Developed efficient crowd-sourcing techniques to gather a dataset of ~1000 publications for analysis
\item Created a tool to calculate the impact factor of any given year within a 15 year range and the magnitude of change if the publication date of the papers in the subset was delayed.
\item Publication submitted
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{IESL Labratory}
\descript{| Research Assistant}

\location{Oct 2015 – Sept 2016 | Amherst, MA}
\begin{tightitemize}
\item Worked under Professor \textbf{\href{https://people.cs.umass.edu/~mccallum/}{Andrew McCallum}} to develop an efficient crowd-sourcing method to extract large lists of information from CVs
\item Designed a pipeline to obtain a knowledge base of 5000+ professors and graduate students to be used in determining conflict of interest for peer reviews.
\item Research was accepted by Massachusetts Statewide Undergraduate Research Conference (April 2016).
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}