\cvsection{Work Experience}
\begin{cventries}
    \vspace{-10pt}
  \cventry
    {Software Engineering Intern}
    {TriNetX, Inc.}
    {Cambridge, MA}
    {May 2017 - Aug. 2017}
    {
      \begin{cvitems}
        \item {Worked with the Infrastructure Team to develop automation and deployment utilities.}
        % resulting in a more defensive design with greater configuration options
        \item {Spearheaded project to improve and increase automation of server provisioning process using Ansible and Python.}
        \item {Created a set of utility scripts in Bash to obtain the health status of servers and make configuration changes as needed.}
        \item{ Performed ad-hoc tasks to improve monitoring and maintenance of AWS using Python and AWS Lambda.}
      \end{cvitems}
    }

\vspace{-18pt}

  \cventry
    {Implementation Analyst Intern}
    {TriNetX, Inc.}
    {Cambridge, MA}
    {May 2016 - May 2017}
    {
      \begin{cvitems}
        \item {Worked with the Client Services and Software Engineering Team to assist in the provider site onboarding process and add customer-requested features.}
        \item {Designed and implemented feature to export audit and query history pages to CSVs using Java.}
        \item{Wrote and tested SQL Scripts to assess the cleanliness of healthcare organizations’ databases.}
        \item{Completed data refreshes, data ingestion, and data mapping of healthcare organizations' data.}
      \end{cvitems}
    }
    
    \vspace{-18pt}

  \cventry
    {Teaching Assistant}
    {University of Massachusetts Amherst}
    {Amherst, MA}
    {Sept. 2016 - May 2017}
    {
      \begin{cvitems}
        \item {Helped teach the introductory computer science course and graded homework submissions by students.}
        \item{Led discussion sections with other TAs and met weekly with the professor to modify and improve discussion sections to suit students’ needs.}
      \end{cvitems}
    }
    \vspace{-18pt}

  \cventry
    {Software Engineering Intern}
    {Yoke.io}
    {Burlington, MA}
    {Dec. 2015 - Jan. 2016}
    {
      \begin{cvitems}
        \item {Integrated multiple third party applications through the implementation of different types of Single Sign-On (SSO) Solutions.}
        \item {Tested the RESTful APIs of third party apps using cURL.}
        \item{Brainstormed ideas for how to integrate third party apps with application.}
      \end{cvitems} 
    }
\end{cventries}
