%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Varan}{Culanathan}{ % Your name
% \urlstyle{same}\url{http://linkedin.com/vculanathan} \\ % Your website, LinkedIn profile or other web address
\footnotesize{ \faMobile \hspace{1mm} { (978)-393-1928 } \hspace{1mm}|\hspace{1mm} \faEnvelope \hspace{1mm} \href{mailto:vculanathan@umass.edu}{ vculanathan@umass.edu }\hspace{1mm}|\hspace{1mm} \faGithub \hspace{1mm} \href{https://github.com/vculanathan}{ github.com/vculanathan} \hspace{1mm}|\hspace{1mm}
\faLinkedinSquare \hspace{1mm} \href{https://www.linkedin.com/in/vculanathan}{linkedin.com/in/vculanathan}} \\% Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{UMass Amherst}

\descript{B.S. in Computer Science}
\location{Expected May 2018 | Amherst, MA }
\location{ Cumulative GPA: 3.98 / 4.00 }




%------------------------------------------------

%------------------------------------------------
% Links
%------------------------------------------------

%------------------------------------------------
% Coursework
%------------------------------------------------
\vspace{1mm}
\descript{Coursework}
Software Engineering \\
Discrete Mathematics \\
Introduction to Probability \\
Functional Programming \\
Data Structures \\


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Languages}


\location{\bf Proficient:}
Java, Python, Bash, SQL, \LaTeX\ \\ 
\vspace{2mm}
\location{\bf Familiar:}
C, Scala, Javascript \\


\sectionspace % Some whitespace after the section

\section{Engineering}


{\bf Infrastructure:}
AWS, Ansible, Docker, Jenkins, Terraform \\  
{\bf Databases:}
MongoDB, SQL \\
{\bf Backend:} 
Node.js \\
{\bf Native:}
Android

\sectionspace % Some whitespace after the section

\section{Awards}
{\bf Course Citation \hfill May 2017} \\ 
\textit{Discrete Mathematics} \\ 
Ranked \#15 in a class of 200+ students.\\
\vspace{2mm}
{\bf Course Citation \hfill Dec 2016} \\ 
\textit{Computer System Principles} \\ 
Ranked \#2 in a class of 150+ students.\\
\vspace{2mm}
{\bf Course Citation \hfill Dec 2015} \\ \textit{Data Structures} \\
 Ranked \#4 in a class of 150+ students.\\
 \vspace{2mm}

\section{Projects} 
{\bf Minesweeper \hfill Jun 2016} \\ A complete version of Minesweeper with fully functionial GUI and custom art. {\it Java} \\
{\bf KeyFinder\hfill Jan 2015} \\ Control a person in a two-dimensional maze to find a hidden key. {\it Java} 
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.65\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Work Experience}

\runsubsection{TriNetX}
\descript{| Software Engineering Intern}
\location{May 2017 – Sep 2017 | Cambridge, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Worked with the Infrastructure Team to develop automation and deployment utilities using Python, Bash, Ansible, Jenkins, and AWS Lambda.
\item Improved and increased automation of appliance provisioning process, resulting in a more defensive design with greater configuration options.
\item Created a set of utility scripts to obtain the health status of appliances based on network connectivity, port connectivity, and NIC bond configuration.
\item Performed ad-hoc tasks to improve monitoring and maintenance of AWS.
\item Assembled server hardware and provisioned servers into appliances for shipment to healthcare organization sites
\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{TriNetX}
\descript{| Implementation Analyst Intern}
\location{May 2016 – May 2017 | Cambridge, MA}
\begin{tightitemize}
\item Worked with the Client Services and Software Engineering Team to assist in the provider site onboarding process and add customer-requested features using SQL and Java.
\item Designed and implemented feature to export audit and query history pages to CSVs. 
\item Wrote and tested SQL Scripts to assess the cleanliness of healthcare organizations’ databases.
\item Completed data refreshes, data ingestion, and data mapping of healthcare organizations' data.
\end{tightitemize}

\sectionspace % Some whitespace after the section
\runsubsection{UMass Amherst}
\descript{| Teaching Assistant }
\location{Sep 2016 – Jan 2017 | Amherst, MA} 
\begin{tightitemize}
\item Helped teach the introductory computer science course offered at UMass.
\item Led discussion sections with other TAs and met weekly with the professor to modify and improve discussion sections to suit students’ needs.
\item Graded homework and project submissions by students.
\end{tightitemize}


%------------------------------------------------

%------------------------------------------------

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{RBR Laboratory}
\descript{| Research Assistant}

\location{Oct 2015 – May 2016 | Amherst, MA}
\begin{tightitemize}
\item Worked under Professor \textbf{\href{http://rbr.cs.umass.edu/shlomo/}{Shlomo Zilberstein}} to investigate the methodology used to calculate the impact factor of a journal.
\item Developed efficient crowd-sourcing techniques to gather a dataset of over 1000 publications from a set of journals for analysis.
\item Created a tool to calculate the impact factor of a journal for any given year and perform basic data analytics to measure how it would be altered in certain situations.
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{IESL Laboratory}
\descript{| Research Assistant}

\location{Oct 2015 – Sep 2016 | Amherst, MA}
\begin{tightitemize}
\item Worked under Professor \textbf{\href{https://people.cs.umass.edu/~mccallum/}{Andrew McCallum}} to develop an efficient crowd-sourcing method to extract large lists of information from CVs.
\item Designed a pipeline to obtain a knowledge base of 5000+ professors and graduate students to be used in determining conflict of interest for peer reviews.
\item Research was accepted by Massachusetts Statewide Undergraduate Research Conference (April 2016).
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
